### 2018-08-31 ms.tex
Edits to methods.

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Madagascar, Senegal and Indonesia as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
Given the available data we chose to focus our analysis on 2012-2015 for Indonesia and 2013-2014 for Madagascar.

@@

The polygon level surveillance data were collated from various government reports.
To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used.
Where species specific reports were given, these were used. 
When reports were no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.

@@

Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data. 
Final population rasters were created by linear interpolation of the surrounding five-yearly rasters

@@

We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres that included land surface temperature annual mean and standard deviation, enhanced vegetation index, mosquito temperature suitability index, elevation, tassel cap brightness, tassel cap wetness, accessibility to cities, night lights and proportion of urban land cover.
Elevation, land surface temperature standard deviation, accessibility to cities and night lights were all log transformed to reduce skewness.
After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables.
The covariates are standardised to have a mean of zero and a standard deviation of one.

@@

We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only prevalence data and 3) the submodel with only aggregated incidence data.

@@

Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < 3) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected, so we set this prior such that the randome field could explain most of the range of the data.

@@

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{ Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, I've covariate would be able to predict prevalences between 0.004 and 0.27. 
This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.

The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}

@@

To compare the three models we used two cross validation schemes. 
In the first, the combined data set of prevalence and incidence data was split into five cross-validation folds stratified by data type.
This reflects real world data where we sometimes have incidence data but no prevalence data and visa versa.
Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2015effect}.

@@

In the second validation scheme the data was split into five spatial cross-validation folds (see Figure~\ref{fig:data}b).
The data was divided by combining the point locations and the centroids of the polygons and performing k means clustering.
This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
Our main performance metric was Pearson's correlation.
However, we also considered Spearman's correlation.
If the prevalence-incidence relationship is poorly estimated, this will strongly affect the Pearson's correlation while the Spearman's correlation will be relatively robust to this source of poor model performance.

>>>>

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
For Indonesia we selected 2010 for prevalence data (n = ) and 2012 for surveillance data (n =).
For Senegal we selected todo for prevalence data (n = ) and todo for surveillance data (n =).
Finally, for Madagascar we selected 2013 for both prevalence (n = ) and surveillance (n = ) data.

@@

The polygon level surveillance data were collated from various government reports.
To account for underreporting of clinical cases due to lack of treatment seeking, missed case reports and cases that sought medical attention outside the public health systems, the methods in \cite{cibulskis2011worldwide} were used.
Where species specific reports were given, these were used. 
For reports where no species specific, national estimates of the ratio between \emph{P. falciparum} and \emph{P. vivax} cases were used to calculate \emph{P. falciparum} only cases.

@@

Raster surfaces of population for the years 2005, 2010 and 2015, were created using a hybrid of data from GPWv4 \cite{gpw4} and WorldPop \cite{tatem2017worldpop}, with the latter taking priority for those pixels where both had population data. 
Final population rasters were created by linear interpolation of the surrounding five-yearly rasters.
Finally, for each year, national population estimates from the UN were raked over the interpolated population surfaces.

@@

We considered an initial suite of environmental and anthropological covariates, at a resolution of approximately $5 \times 5$ kilometres that included land surface temperature annual mean and standard deviation, enhanced vegetation index, mosquito temperature suitability index, elevation, tassel cap brightness, tassel cap wetness, accessibility to cities, night lights and proportion of urban land cover.
Elevation, land surface temperature standard deviation, accessibility to cities and night lights were all log transformed to reduce skewness.
After preliminary analyses, tassel cap brightness and urban land cover were removed as they were highly correlated with other variables.
The covariates were standardised to have a mean of zero and a standard deviation of one.

@@

We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only prevalence data and 3) the submodel with only aggregated incidence data. 
The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}

@@

Finally, we complete the model by setting priors on the parameters $\beta_0, \beta, \rho$ and $\sigma_u$, $\sigma_v$ and $\sigma_w$.
We assigned $\rho$ and $\sigma_u$ a joint penalised complexity prior \cite{fuglstad2018constructing} such that $P(\rho < \zeta) = 0.00001$ and $P(\sigma_u > 1) = 0.00001$.
We used different $\zeta$ values for each country: Indonesia $\zeta = 3$, Senegal $\zeta = todo$ and Madagascar $\zeta = 1$.
We believe that a large proportion of the variance of malaria prevalence and incidence cannot be explained by a linear combination of the covariates selected \cite{bhatt2017improved}, so we set this prior such that the random field could explain most of the range of the data.

@@

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{ Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.

@@

To compare the three models we used two cross validation schemes. 
In the first, the combined data set of prevalence and incidence data was split into ten cross-validation folds stratified by data type.
This reflects real world data where we in some locations we have incidence data but no prevalence data and visa versa.
Thus this cross-validation scheme can be seen as asking whether aggregated incidence data provides a viable or preferable alternative to using just prevalence data as in previous modelling efforts \cite{bhatt2015effect}.

@@

In the second validation scheme the data was split into spatial cross-validation folds (see Figure~\ref{fig:data}b).
The number of folds was seven for Indonesia, todo for Senegal and three for Madagascar due to their differing size and geography.
The data was divided by combining the point locations and the centroids of the polygons and performing k means clustering.
This scheme is testing the models' ability to predict into new areas with little information from the spatial random field.

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
Our main performance metric was Pearson's correlation.
However, we also considered Spearman's correlation.
If the prevalence-incidence relationship is poorly estimated, this will strongly affect the Pearson's correlation while the Spearman's correlation will be relatively robust to this source of poor model performance.
Finally, we considered coverage of the 80\% credible intervals.
